---
title: "DEDUCE Dose Escalation Recommendations"
output: word_document
params:
  df1: NA
  df2 :NA
  r1: NA
  r2: NA
  r3: NA
  r4: NA
  r5: NA
  r6: NA
  r7: NA
  r8: NA
  r9: NA
---
*Report Date and Time: "`r Sys.time()`"*

**`r params$d`**

*Software:* DEDUCE app version 1.0 available [here](https://bengarski.shinyapps.io/DEDUCE/) 


# Data Summary:

```{r, echo=FALSE, fig.cap="Figure 1: }
params$df1 + theme(text = element_text(size = 12))  
```


# Toxicity Probability Update (with 90 Percent Probability Interval):
```{r, echo=FALSE, fig.cap="Figure 2:"}
params$df2 + theme(text = element_text(size = 12))  
```

## Next Recommended Dose Level: "`r params$r1`"

## Recommendation is Based on a Target Toxicity Probability of "`r params$r2`"

## Estimation Details:
Empiric Dose-Toxicity Model: $p = dose^{exp(beta)}$
dose = "`r params$r3`"

## Normal Prior on Beta with Mean 0 and Variance "`r params$r4`"

## Posterior Mean of Beta: "`r params$r5`"

## Posterior Variance of Beta: "`r params$r6`"

# Additional Details:

## Current Dose Level: "`r params$r7`"

## Cohort Size: "`r params$r8`"

## Number of Slots Remaining at Current Dose Level: "`r params$r9`"

## Dose Escalation Rules:
* No dose skipping upon dose escalation
* Intra-cohort dose de-escalation is allowed
* Intra-cohort dose escalation is not allowed
