---
title: "DEDUCE Simulated Operating Characteristics of Phase 1 Dose Escalation Designs"
output: word_document
params:
  d: NA
  m: NA
  r: NA
  t: NA
  p1: NA
  p2: NA
  p3: NA
  p4: NA
---
*Report Date and Time: "`r Sys.time()`"*

*Software:* DEDUCE app version 1.0 available [here](https://bengarski.shinyapps.io/DEDUCE/) 


# Objective:

To evaluate the operating characteristics of the following dose escalation design(s): **`r params$d`**

# Methods:

Trial operating characteristics are averaged over **`r params$m[1]`** simulated trials. Simulated trials have **`r params$m[2]`** dose levels labeled **`r params$m[3]`**, starting on the dose labeled as **`r params$m[4]`**, and assuming true toxicity probabilities of **`r params$m[5]`**. The target toxicity probability is **`r params$m[6]`**. One patient arrives every **`r params$m[7]`** days on average. The DLT observation period is **`r params$m[8]`** days.

<!-- Test if TARGET-CRM/CRM is a Design Used -->
```{r, echo=FALSE}
if("TARGET-CRM" %in% params$d | "CRM" %in% params$d) {
  show_text_methods <- TRUE
}else{
  show_text_methods <- FALSE
}
```

<!-- Only Show if TARGET-CRM/CRM is Selected -->
`r if(!show_text_methods) {"<!--"}`

For the TARGET-CRM and/or CRM design, the prior toxicity probabilities per dose level are **`r params$m[9]`**. The cohort size is **`r params$m[10]`** and the maximum sample size is **`r params$m[11]`**. Patients belong to one of two cohorts: Cohort A or Cohort B. Patients with pre-specified characteristics (e.g. tumor type, tumor mutation) belong to Cohort B; all other patients belong to Cohort A. The TARGET-CRM design allows enrollment of Cohort B patients at one dose level below the current dose during the DLT observation period of the current cohort of patients. The proportion of patients from Cohort B is **`r params$m[12]`**. Simulated trials using the TARGET-CRM and/or CRM designs are required to have a minimum enrollment of **`r params$m[13]`** Cohort B patients.


`r if(!show_text_methods) {"-->"}`

# Results:

<!-- Test if TARGET-CRM is a Design Used -->
```{r, echo=FALSE}
if("TARGET-CRM" %in% params$d) {
  show_text_results <- TRUE
}else{
  show_text_results <- FALSE
}
```

<!-- Test if 1 Design Used -->
```{r, echo=FALSE}
if(length(params$d)==1) {
  show_text_results2 <- TRUE
}else{
  show_text_results2 <- FALSE
}
```

<!-- Only Show if 1 Design Used -->
`r if(!show_text_results2) {"<!--"}`

**Accuracy:** For each dose level, Figure 1 presents the proportion of simulated trials that a given dose level was selected as the true MTD. The proportion of correct selection (PCS) of the MTD for the **`r params$d`** design is **`r params$r[1]`**.

**Safety:** Figure 2 presents the proportion of patients experiencing a DLT for each dose level. The proportion of patients experiencing a DLT for the **`r params$d`** design is **`r params$r[2]`** which is **`r params$r[4]`** than the target toxicity probability of **`r params$r[3]`**

**Patient Allocation:** Figure 3 presents the proportion of patients assigned to each dose level. The proportion of patients assigned to the true MTD (dose level **`r params$r[5]`**) for the **`r params$d`** design is **`r params$r[6]`**.

**Study Duration:** Figure 4 presents the mean (+/- standard deviation) study duration in days for each design. The mean study duration for the **`r params$d`** design is **`r params$r[7]`** (standard deviation = **`r params$r[8]`**).

Table 1 presents a summary of the operating characteristics for each design.

**Sample Size:** The mean total sample size for the **`r params$d`** design is **`r params$r[9]`** (range = **`r params$r[10]`**-**`r params$r[11]`**).

`r if(!show_text_results2) {"-->"}`

<!-- Only Show if 2+ Designs Used -->
`r if(show_text_results2) {"<!--"}`

**Accuracy:** For each dose level, Figure 1 presents the proportion of simulated trials that a given dose level was selected as the true MTD. The **`r params$r[1]`** design has the greatest probability of selecting the true MTD (dose level **`r params$r[2]`**). `r params$r[3]`

**Safety:** Figure 2 presents the proportion of patients experiencing a DLT for each dose level. `r params$r[4]`

**Patient Allocation:** Figure 3 presents the proportion of patients assigned to each dose level. The **`r params$r[5]`** design has the greatest probability of assigning patients at the true MTD (dose level **`r params$r[2]`**). `r params$r[6]`

**Study Duration:** Figure 4 presents the mean (+/- standard deviation) study duration in days for each design. The **`r params$r[7]`** design has the shortest mean study duration. `r params$r[8]`

Table 1 presents a summary of the operating characteristics for each design.

**Sample Size:** `r params$r[9]`

`r if(show_text_results2) {"-->"}`

# Figures:

```{r, echo=FALSE, fig.cap="Figure 1: Proportion of simulated trials selecting each dose level as the true MTD."}
params$p1 + theme(text = element_text(size = 12))  
```

```{r, echo=FALSE, fig.cap="Figure 2: Proportion of patients experiencing a DLT per dose level. The target toxicity probability is denoted by the horizontal dashed line."}
params$p2 + theme(text = element_text(size = 12)) 
```

```{r, echo=FALSE, fig.cap="Figure 3: Proportion of simulated trials selecting each dose level as the true MTD."}
params$p3 + theme(text = element_text(size = 12)) 
```

```{r, echo=FALSE, fig.cap="Figure 4: The mean (+/- 1 standard deviation) study duration in days."}
params$p4 + theme(text = element_text(size = 12)) 
```

<br><br><br><br>

```{r, echo=FALSE}
knitr::kable(params$t, caption = "Table 1: Summary of operating characteristics for the selected designs.")
```

