---
title: "DEDUCE Dose Escalation Recommendations"
output: word_document
params:
  d: NA
  df1: NA
  df2: NA
  r1: NA
  r2: NA
  r3: NA
  r4: NA
  r5: NA
  r6: NA
  r7: NA
  r8: NA
  r9: NA
---

Trial Design: `r params$d`\
Software: DEDUCE app version 1.0 available [here](https://wendyblondon.shinyapps.io/DEDUCE/)\
Report Date and Time: `r paste(lubridate::with_tz(Sys.time(), "America/New_York"), 'ET')`\

# Observed Toxicity Data:

```{r, echo=FALSE}
knitr::kable(params$df1, col.names = c("Patient ID", "Dose Level", "Experienced a DLT", "Included in Model"))
```


# Toxicity Probability Results:
```{r, echo=FALSE}
knitr::kable(params$df2, col.names = c("Dose Level", "Prior Toxicity Prob.", "n", "# Experienced a DLT", "Posterior Toxicity Prob.", "Lower Limit of 90% Prob. Interval", "Upper Limit of 90% Prob. Interval"), caption = "(90 Percent Probability Interval)")
```

Next Recommended Dose Level: `r params$r1`

Recommendation is Based on a Target Toxicity Probability of `r params$r2`

# Additional Details:

Current Dose Level: `r params$r7`

Cohort Size: `r params$r8`

Number of Slots Remaining at Current Dose Level: `r params$r9`

# Dose Escalation Rules:

* No dose skipping upon dose escalation
* Intra-cohort dose de-escalation is allowed
* Intra-cohort dose escalation is not allowed

# Estimation Details:

Empiric Dose-Toxicity Model: $p = dose^{exp(beta)}$\
dose = `r params$r3`

Normal Prior on Beta with Mean 0 and Variance `r params$r4`

Posterior Mean of Beta: `r params$r5`

Posterior Variance of Beta: `r params$r6`
